Manuscript

### 2015-02-21 inst/simulation/manuscript.Rmd
...

p <- ggplot(densitiesScaled) + geom_raster(aes_string(x="x", y="y", fill=yearLayer)) +
  scale_fill_gradientn(colours=terrain.colors(100), na.value="transparent", guide=guide_legend(title=expression(paste("Population density ", (log[10]~individuals/km^2)))), trans="log10", breaks=c(10^-4.5, 10^-4, 10^-3.5, 10^-3, 10^-2.5), labels=c(expression(10^-4.5), expression(10^-4.0), expression(10^-3.5), expression(10^-3.0), expression(10^-2.5)), limits=(10^-4.5, 10^-2.5)) +
  geom_path(data=boundaryDF, aes(long, lat, group=group), colour="darkgreen") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1.3, colour="white") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1) + scale_color_manual(values=c("darkgray", "black"), guide=FALSE) +
  scale_x_continuous(limits=c(limits@xmin, limits@xmax), expand=c(0,0)) +
  scale_y_continuous(limits=c(limits@ymin, limits@ymax), expand=c(0,0)) +
  facet_grid(~scenario) + coord_equal() + theme_raster(base_size=10) + theme(legend.position="bottom")
#print(p)
#saveFigure(p, "manuscript-figure-2a.png", width=6,height=3)
saveFigure(p, "manuscript-figure-2a.png", width=17, height=8, dpi=200) # draft quality

@@

p <- ggplot(boundaryDF) + geom_path(aes(long, lat, group=group), colour="grey") +
  geom_point(data=surveyRoutes, aes(x, y, colour=intersections), size=1) + scale_color_manual(values=c("darkgrey", "black")) +
  scale_x_continuous(breaks=seq(gridTemplate@extent@xmin, gridTemplate@extent@xmax, 1e5), expand=c(0,0)) +
  scale_y_continuous(breaks=seq(gridTemplate@extent@ymin, gridTemplate@extent@ymax, 1e5), expand=c(0,0)) +
  facet_grid(~scenario) + theme_raster(base_size=10) + coord_equal() + theme(panel.grid.major=element_line(colour="grey"))
print(p)
#saveFigure(p, "manuscript-figure-2b.png", width=6,height=3)
saveFigure(p, "manuscript-figure-2b.png", width=17, height=8, dpi=200) # draft quality

@@

plotLogPopulationSize <- function(size, modelName, xlim, ylim) {
  library(ggplot2)
  library(scales)  
  size$Scenario <- prettyScenario(size$Scenario)
  meanSize <- getMeanPopulationSizes(size)
  meanSize$Scenario <- prettyScenario(meanSize$Scenario)

@@

  p <- p + facet_wrap(~Scenario) +
    scale_x_continuous(limits=xlim, labels=trans_format("identity", math_format(10^.x))) +
    scale_y_continuous(limits=ylim, labels=trans_format("identity", math_format(10^.x))) +
    xlab("True population size") + ylab("Estimated population size") + ggtitle(paste("Model: ", prettyModelName(modelName[1]))) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"),
                                        plot.title=element_text(size=10),
                                        plot.margin=unit(c(0, 0, 0, 0), units="line"), #top, right, bottom, and left margins
                                        legend.margin=unit(0, units="line"),
                                        panel.margin=unit(0, units="line"))

@@

```{r figure-3-init-2-test, eval=FALSE}
populationSizes <- getPopulationSizes(scenarios=scenarios[1:4], modelNames=modelNames[3:4])
populationSizes2000 <- getPopulationSizes(scenarios=paste0(scenarios[1:4], "combined"), modelNames=modelNames[3:4])
populationSizes10Days <- getPopulationSizes(scenarios=paste0(scenarios[1:4], "10days"), modelNames=modelNames[3:4])
```

@@

xlim <- log10(c(1,6000)); ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a1.png")
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a2.png")
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[4]), modelName=modelNames[4], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a3.png")

p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b1.png")
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b2.png")
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[4]), modelName=modelNames[4], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b3.png")

p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c1.png")
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c2.png")
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[4]), modelName=modelNames[4], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c3.png")
```

@@

```{r table-2}
plotIntersectionPopulationSizeTable <- function(ratioTable) {
  library(reshape2)
  library(grid)
  x <- melt(ratioTable, id.vars=c("Scenario", "Case"), measure.vars=c("SizeCount"))
  p <- ggplot(x, aes(Scenario, value, group=Case)) + geom_point(aes(shape=Case)) + geom_line() +
    ylab("") + #guides(shape=guide_legend()) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"), legend.title=element_text(size=10),
                                        strip.text.y=element_text(size=10), legend.position="bottom",
                                        plot.margin=unit(c(0, 0, -.5, -.5), units="line"),
                                        legend.margin=unit(0, units="line"),
                                        panel.margin=unit(0, units="line"))# , legend.key=element_rect(fill="transparent"))
  return(p) 
}
p <- plotIntersectionPopulationSizeTable(iall)
saveFigure(p, "manuscript-figure-4x.png")

@@

rer.stat <- function(x) data.frame(SizeCount=round(mean(x$intersections/x$Observed),2), SizeCountSD=round(sd(x$intersections/x$Observed),2))
i <- ddply(intersectionsx, .(Scenario), rer.stat); i$Scenario=prettyScenario(i$Scenario); i$Case <- "a"
i2000 <- ddply(intersections2000x, .(Scenario), rer.stat); i2000$Scenario=prettyScenario(i2000$Scenario); i2000$Case <- "b"
i10days <- ddply(intersections10daysx, .(Scenario), rer.stat); i10days$Scenario=prettyScenario(i10days$Scenario); i10days$Case <- "c"

iall <- rbind(i, i2000, i10days)
p <- plotIntersectionPopulationSizeTable(iall)
saveFigure(p, "manuscript-figure-4x.png")

@@

plotPopulationCorrelations <- function(populationCorrelations) {
  populationCorrelations$Scenario <- prettyScenario(populationCorrelations$Scenario)
  p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  scale_y_continuous(limits=c(-1,1)) +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"),
                                      plot.margin=unit(c(0, 0, -.5, -.5), units="line"),
                                      legend.margin=unit(0, units="line"),
                                      panel.margin=unit(0, units="line"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
  return(p)
}
```

@@

p1 <- plotPopulationCorrelations(pc1)
saveFigure(p1, "manuscript-figure-4a.png")
p2 <- plotPopulationCorrelations(pc2)
saveFigure(p2, "manuscript-figure-4b.png")
p3 <- plotPopulationCorrelations(pc3)
saveFigure(p3, "manuscript-figure-4c.png")
```

@@

plotCIProportions <- function(credibilityIntervals) {
  modelLabels <- prettyModelName(unique(credibilityIntervals$modelName))
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=CI, colour=modelName)) +
    geom_hline(aes(yintercept=.5), color="grey90") +
    geom_hline(aes(yintercept=.95), color="grey90") +
    geom_point() +
    scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("black", "darkgray"), labels=modelLabels) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion within CI") +
    facet_wrap(~panel) + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
          plot.margin=unit(c(0, 0, -.5, -.5), units="line"),
          legend.margin=unit(0, units="line"),
          panel.margin=unit(0, units="line"),
          legend.position="bottom")
  return(p)
}
```

@@

cip <- subset(rbind(cip1, cip2, cip3), modelName != "SmoothModel-nbinomial-ar1")
p <- plotCIProportions(cip)
saveFigure(p, "manuscript-figure-5.png", width=6, height=2)
```

>>>>

#library(directlabels)

p <- ggplot(densitiesScaled) +
  geom_raster(aes_string(x="x", y="y", fill=yearLayer)) +
  stat_contour(aes_string(x="x", y="y", z=yearLayer, colour=yearLayer), size=0.1)
#p <- direct.label(p)
p <- p + scale_fill_gradientn(colours=terrain.colors(100), na.value="transparent",
                       guide=guide_legend(title=expression(paste("Log population density ", (individuals/km^2)))), trans="log10",
                       #breaks=c(10^-4.5, 10^-4, 10^-3.5, 10^-3, 10^-2.5),
                       breaks=trans_breaks("log10", function(x) 10^x),
                       #labels=c(expression(10^-4.5), expression(10^-4.0), expression(10^-3.5), expression(10^-3.0), expression(10^-2.5)), limits=c(10^-4.5, 10^-2.5)
                       labels=trans_format("log10", math_format(10^.x))
                       ) +
  geom_path(data=boundaryDF, aes(long, lat, group=group), colour="darkgreen") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1.3, colour="white") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1) + scale_color_manual(values=c("darkgray", "black"), guide=FALSE) +
  scale_x_continuous(limits=c(limits@xmin, limits@xmax), expand=c(0.01,0.01)) +
  scale_y_continuous(limits=c(limits@ymin, limits@ymax), expand=c(0.01,0.01)) +
  facet_grid(~scenario) + coord_equal() + theme_raster(base_size=10) +
  theme(legend.position="bottom", legend.margin=unit(-2, units="line"),
        plot.margin=unit(c(-.5, 0, 0, -.5), units="line"))
#p <- direct.label(p)
saveFigure(p, "manuscript-figure-2a.png", width=17, height=7.2, dpi=200) # draft quality

@@

p <- ggplot(boundaryDF) + geom_path(aes(long, lat, group=group), colour="grey") +
  geom_point(data=surveyRoutes, aes(x, y, colour=intersections), size=1) + scale_color_manual(values=c("darkgrey", "black")) +
  scale_x_continuous(breaks=seq(gridTemplate@extent@xmin, gridTemplate@extent@xmax, 1e5), expand=c(0,0)) +
  scale_y_continuous(breaks=seq(gridTemplate@extent@ymin, gridTemplate@extent@ymax, 1e5), expand=c(0,0)) +
  facet_grid(~scenario) + theme_raster(base_size=10) + coord_equal() +
  theme(panel.grid.major=element_line(colour="grey"), plot.margin=unit(c(0, 0, 0, -.5), units="line"))
saveFigure(p, "manuscript-figure-2b.png", width=17, height=6.7, dpi=200) # draft quality

@@

plotLogPopulationSize <- function(size, modelName, case, xlim, ylim) {
  library(ggplot2)
  library(scales)  
  size$Scenario <- prettyScenario(size$Scenario)
  meanSize <- getMeanPopulationSizes(size)
  meanSize$Scenario <- prettyScenario(meanSize$Scenario)

@@

  p <- p + facet_wrap(~Scenario) +
    scale_x_continuous(limits=xlim, labels=trans_format("identity", math_format(10^.x))) +
    scale_y_continuous(limits=ylim, labels=trans_format("identity", math_format(10^.x))) +
    xlab("Log true population size") + ylab("Log estimated population size") + ggtitle(paste("Case:", case, " Model:", prettyModelName(modelName[1]))) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"),
                                        plot.title=element_text(size=10),
                                        plot.margin=unit(c(0, 0, 0, 0), units="line"), #top, right, bottom, and left margins
                                        legend.margin=unit(0, units="line"),
                                        panel.margin=unit(0, units="line"))

@@

@@

xlim <- log10(c(1,6000)); ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[1]), modelName=modelNames[1], "a", xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a1.png")
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[3]), modelName=modelNames[3], "a", xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a2.png")
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[4]), modelName=modelNames[4], "a", xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a3.png")

p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[1]), modelName=modelNames[1], "b", xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b1.png")
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[3]), modelName=modelNames[3], "b", xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b2.png")
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[4]), modelName=modelNames[4], "b", xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b3.png")

p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[1]), modelName=modelNames[1], "c", xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c1.png")
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[3]), modelName=modelNames[3], "c", xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c2.png")
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[4]), modelName=modelNames[4], "c", xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c3.png")
```

@@

```{r table-2}
plotIntersectionPopulationSizeTable <- function(ratioTable) {
  library(reshape2)
  library(grid)
  x <- melt(ratioTable, id.vars=c("Scenario", "Case"), measure.vars=c("SizeCount"))
  p <- ggplot(x, aes(Scenario, value, group=Case)) + geom_point(aes(shape=Case)) + geom_line() +
    ylab("Ratio") + #guides(shape=guide_legend()) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"), legend.title=element_text(size=10),
                                        strip.text.y=element_text(size=10), legend.position="right",
                                        #legend.background=element_rect(fill="transparent"),
                                        plot.margin=unit(c(0.2, 0, 0, 0), units="line"),
                                        legend.margin=unit(-1, units="line"),
                                        panel.margin=unit(0, units="line"))# , legend.key=element_rect(fill="transparent"))
  return(p) 
}

@@

rer.stat <- function(x) data.frame(SizeCount=mean(x$intersections/x$Observed), SizeCountSD=sd(x$intersections/x$Observed))
i <- ddply(intersectionsx, .(Scenario), rer.stat); i$Scenario=prettyScenario(i$Scenario); i$Case <- "a"
i2000 <- ddply(intersections2000x, .(Scenario), rer.stat); i2000$Scenario=prettyScenario(i2000$Scenario); i2000$Case <- "b"
i10days <- ddply(intersections10daysx, .(Scenario), rer.stat); i10days$Scenario=prettyScenario(i10days$Scenario); i10days$Case <- "c"

iall <- rbind(i, i2000, i10days)
p <- plotIntersectionPopulationSizeTable(iall)
saveFigure(p, "manuscript-figure-4x.png", height=7.87/2.5)

@@

plotPopulationCorrelations <- function(populationCorrelations, case) {
  populationCorrelations$Scenario <- prettyScenario(populationCorrelations$Scenario)
  p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  scale_y_continuous(limits=c(-1,1)) +
  ggtitle(paste("Case:", case)) +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"),
                                      plot.title=element_text(size=10),
                                      plot.margin=unit(c(0, 0, 0, 0), units="line"),
                                      panel.margin=unit(0, units="line"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
  return(p)
}
```

@@

p1 <- plotPopulationCorrelations(pc1, "a")
saveFigure(p1, "manuscript-figure-4a.png")
p2 <- plotPopulationCorrelations(pc2, "b")
saveFigure(p2, "manuscript-figure-4b.png")
p3 <- plotPopulationCorrelations(pc3, "c")
saveFigure(p3, "manuscript-figure-4c.png")
```

@@

plotCIProportions <- function(credibilityIntervals) {
  modelLabels <- prettyModelName(unique(credibilityIntervals$modelName))
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=CI, colour=modelName)) +
    geom_hline(aes(yintercept=.5), color="grey90") +
    geom_hline(aes(yintercept=.95), color="grey90") +
    geom_point() +
    scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("black", "darkgray"), labels=modelLabels) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion") +
    facet_wrap(~panel) + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
          plot.margin=unit(c(0, 0, 0, 0), units="line"),
          #legend.background=element_rect(fill="transparent"),
          legend.margin=unit(-2, units="line"),
          panel.margin=unit(0, units="line"),
          legend.position="bottom",
          legend.box="horizontal")
  return(p)
}
```

@@

cip <- subset(rbind(cip1, cip2, cip3), modelName != "SmoothModel-nbinomial-ar1")
p <- plotCIProportions(cip)
saveFigure(p, "manuscript-figure-5.png", height=7.87/2)
```
